On the analytic structure of the linear response susceptibility in open systems

### 2018-05-03 AnalyticStructure_main.tex
update

From the theoretical analysis of the previous section we can made two statements:
\begin{itemize}
 \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
 wave functions for higher values of $\omega$. 
 \item The excitation landscape is composed of two sectors with distinct properties. One made of a discrete set of localized excitations 
\end{itemize}

Discuss the criterion for a good choice of the basis of transition. Computation of the statical polarizability in the LR formalism compared to the reference value
obtained through a finite difference method. Remark the importance of using a systematic basis, only in this way the convergence of the statical polarizability turns out to 
be a meaningful criterion for the evaluation of the basis that sample the empty state space. Refer to the paper of....

>>>>

From the theoretical analysis of the previous section we can made two statements:
\begin{itemize}
 \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
 wave functions for higher values of $\omega$. 
 \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
 poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
 an effective representation of the spectral function. 
\end{itemize}
The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
if so, up to which energy threshold can we assume that our computations do converge?

The first element of this discussion is the introduction of the computational basis $\{\mu\}$ used to perform the DFT calculations subjacent to the LR analysis. This basis is composed by a 
finite set of elements (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) that are chosen to ensure an unbiased description 
of the ground state properties of the system.

FIRST QUESTION: The usage of the $\{\mu\}$ basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?). 
We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend this reliability of the result up to
$\omega=|\eps_p|$.

SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
the $\{\mu\}$ basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of 
$\bra{\psi_p}\op O$, in this case the computational setup provides reliable results if guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. 
In this range there is no a priori indicator of the goodness of the results.

%\vspace{0.3cm}
\subsection{Choice of the $\alpha$-basis. Statical polarizability-driven criterion revised}

The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\{\mu\}$ 
basis. Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.

The construction of the excitation operators requires the explicit sampling of the empty state subspace. Definition of the $\{\alpha\}$-basis: choose the empty eigenstates of the KS Hamiltonian as a 
basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. The elements $\{\alpha\}$-basis are expressed in the $\{\mu\}$-basis: since the $\{\mu\}$-basis is finite 
dimensional so it is also the $\{\alpha\}$-basis. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.

% Discuss the criterion for a good choice of the basis of transition. Computation of the statical polarizability in the LR formalism compared to the reference value obtained through a finite 
% difference method. Remark the importance of using a systematic basis, only in this way the convergence of the statical polarizability turns out to be a meaningful criterion for the evaluation 
% of the basis that sample the empty state space. Refer to the paper of....
